### 2020-02-03 all_models.tex
updating sec 6

To further refine our analysis, we run three batches of linear regressions. First at the global level, we divide models by datasets and run regression separately on all models of a certain dataset, regardless of the architecture. At this level, the plots are quite noisy and clustered as each architecture has its own accuracy trend but, you could still see that most plots show positive relationship with positive coefficients

\serena{see examples in Figure X}

(Here we omit the results for CUB-200-2011, Pascal-VOC2012, ADE20K, and COCO datasets as there are less than 15 models for those datasets and thus the regression is less statistically significant)

\serena{insert plots for Figure X}

For the second batch, we plot the regression for models of each architecture-datasets combination, which shows the relationship between the progression of the model accuracy and Weightwatcher metrics more clearly and precisely. For example, as you could see in the Figure X2,

\serena{Add an example, UPDATE when we have the results from the new codes}

Insert plots for Figure X2

While running each regression, we record the R-squared and mean squared errors (MSE) for each regression. We then filter out regressions with less than five datapoints and models with structural outliers.

\serena{Define and give an example of the structural outliers}

Insert a plot for outliers, OPTIONAL

@@

\charles{Still preliminary, only 309 data points here}
\paragraph{Results}
\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|}
\hline
%    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
%    & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\langle\hat{\alpha}=\alpha\log\lambda_{max}\rangle$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
        & Log                   & Log                        & Weighted       & Log                                 \\
        & $\Vert\cdot\Vert_{F}$ & $\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
 Series & Metric                & Metric                     & Metric         & Metric                              \\
\hline
$R^{2}$ (mean) & 0.63 &0.55 &0.64 &0.64 \\
$R^{2}$ (std)  & 0.34 &0.36 &0.29 &0.30 \\
\hline
$MSE$ (mean)   & 4.54 &9.62 &3.14 &2.92 \\
$MSE$ (std)    & 8.69 &23.06 &5.14 &5.00 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of linear regression fits for different average log norm metrics across 5 computer vision datasets, 17 Architectures, covering 168 (out of 309) different pretrained DNNs.  We only conclude regressions for architecturs with 4 or more data points \charles{and which are postively correlated with the test error?}.  These results can be readily reproduced using the Google Colab notebooks accompanying thie paper~\cite{notebooks}}
\label{table:results}
\end{table}

>>>>

%To further refine our analysis, we run three batches of linear regressions. First at the global level, we divide models by datasets and run regression separately on all models of a certain dataset, regardless of the architecture. At this level, the plots are quite noisy and clustered as each architecture has its own accuracy trend but, you could still see that most plots show positive relationship with positive coefficients

%\serena{see examples in Figure X}

%(Here we omit the results for CUB-200-2011, Pascal-VOC2012, ADE20K, and COCO datasets as there are less than 15 models for those datasets and thus the regression is less statistically significant)

%\serena{insert plots for Figure X}

%e compite the regression R-squared and RMSE  for models of each architecture-datasets combination, which shows the relationship between the progression of the model accuracy and Weightwatcher metrics more clearly and precisely. For example, as you could see in the Figure X2,

%\serena{Add an example, UPDATE when we have the results from the new codes}

For each regression, we record the R-squared and mean squared errors (MSE). We filter out regressions with less than five datapoints,
 \nred{and models with structural outliers (where the trend is anti-correlated?) ?}

@@

\charles{Still preliminary, only 309 data points here}
\paragraph{Results}
\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|}
\hline
%    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
%    & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\langle\hat{\alpha}=\alpha\log\lambda_{max}\rangle$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
Series        & $\log\Vert\cdot\Vert_{F}$ & $\log\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\log\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
\hline
$R^{2}$ (mean) & 0.63 &0.55 &0.64 &0.64 \\
$R^{2}$ (std)  & 0.34 &0.36 &0.29 &0.30 \\
\hline
$MSE$ (mean)   & 4.54 &9.62 &3.14 &2.92 \\
$MSE$ (std)    & 8.69 &23.06 &5.14 &5.00 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of linear regression fits for different average log norm metrics across 5 computer vision datasets, 17 Architectures, covering 168 (out of 309) different pretrained DNNs.  We only conclude regressions for architecturs with 4 or more data points \charles{and which are postively correlated with the test error?}.  These results can be readily reproduced using the Google Colab notebooks accompanying thie paper~\cite{notebooks}}
\label{table:results}
\end{table}
